Analytic consideration of the society by itself

### 2017-11-13 latex/nuvem/nuvem1.tex
adicionada primeira versao do artigo p nuvem
incorporada contribs da marilia no nuvem1

\documentclass[letterpaper,10pt]{article}
\usepackage{nuvem}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref} 	%% Use to fix Figure or Table: ex: \begin{table}[H]
\hypersetup{
	%pagebackref=true,
	pdfcreator={LaTeX with abnTeX2},
	pdfkeywords={abnt}{latex}{abntex}{USPSC}{trabalho acadêmico}, 
	colorlinks=true,       		% false: boxed links; true: colored links
	linkcolor=blue,          	% color of internal links
	citecolor=blue,        		% color of links to bibliography
	filecolor=magenta,      		% color of file links
	urlcolor=blue,
	allbordercolors=black,
	bookmarksdepth=4
}
\usepackage[utf8]{inputenc}

@@

On the critical theory tradition,
Marcuse have a central role on
questioning the conditions
imposed for living by technological advances~\cite{m1,m2,m3}.
And the consideration of the authoritarian personality traces~\cite{au}
have gained relevance due to unforeseen social phenomena
such as the recent and worldwide rise of the right-winged manifestations
and political representation~\cite{rise,rise2}.

@@

We also considered the cold-blooded reception of the reality
enabled technologial devices such as drones~\cite{drones}.
(((últimos trabalhos marilia, e.g. impulso,
talvez com foco em tecnologia, talvez passar
este parágrafo para o último e fechar a seção com ele))))

@@

\bibitem{au}
	Adorno, T. W., Frenkel-Brunswik, E., Levinson, D. J., \& Sanford, R. N. (1950). The authoritarian personality.

@@

>>>>

\documentclass[letterpaper,10pt]{article}
\usepackage{nuvem}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
	%pagebackref=true,
	pdfcreator={LaTeX with abnTeX2},
	pdfkeywords={abnt}{latex}{abntex}{USPSC}{trabalho acadêmico}, 
	colorlinks=true,       		% false: boxed links; true: colored links
	linkcolor=blue,          	% color of internal links
	citecolor=blue,        		% color of links to bibliography
	filecolor=magenta,      		% color of file links
	urlcolor=blue,
	allbordercolors=black,
	bookmarksdepth=4
}
\usepackage[utf8]{inputenc}

@@

On the critical theory tradition,
Marcuse have a central role on
questioning the conditions
imposed for living by technological advances~\cite{m1,m2,m3,m4}.
And the consideration of the authoritarian personality traces~\cite{au}
have gained relevance due to unforeseen social phenomena
such as the recent and worldwide rise of the right-winged manifestations
and political representation~\cite{rise,rise2}.

@@

Violence, prejudice and authoritarianism,
and the authoritarian personality and technology,
are frequently co-occurring themes in the two dossier of the
Nexos Networks for Critical Theory and Interdisciplinary Research~\cite{nexos1}.
We also considered the cold-blooded reception of the reality
enabled technological devices such as drones~\cite{drones}.

@@

\bibitem{m1}
	Marcuse, H. (2013). One-dimensional man: Studies in the ideology of advanced industrial society. Routledge.

\bibitem{m2}
	Marcuse, H. (2009). A responsabilidade da ciência. Scientiae studia, 7(1), 159-164.

\bibitem{m3}
	Marcuse, H. (2004). Technology, War and Fascism: Collected Papers of Herbert Marcuse (Vol. 1). Routledge.

\bibitem{m4}
	Pisani, M. M. (2009). Algumas considerações sobre ciência e política no pensamento de Herbert Marcuse. Scientiae Studia, 7(1), 135-158.
\bibitem{au}
	Adorno, T. W., Frenkel-Brunswik, E., Levinson, D. J., \& Sanford, R. N. (1950). The authoritarian personality.

@@

\bibitem{drones}
	Pisani. M.
	Entre Drones e Ciborgues: algumas considerações sobre teoria crítica e a necroética das redes sociais. Revista Impulso, Nov/2017.

\bibitem{nexos1}
	Pisani. M.
	Entre Drones e Ciborgues: algumas considerações sobre teoria crítica e a necroética das redes sociais. Revista Impulso, Nov/2017.

\bibitem{nexos2}
	Dossies of the Nexos Network for Critical Theory and Interdisciplinary Research. Available at: \url{https://www.metodista.br/revistas/revistas-unimep/index.php/impulso/issue/view/207} and \url{https://www.metodista.br/revistas/revistas-unimep/index.php/impulso/issue/view/207}
